Of judges, aliens and total preorders

### 2021-02-12 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: slides structure

@@

\section{Additional metadata for tpo revision}
\section{Booth and Meyer tpo-revision operators}
\section{Iterating: $\preceq$-revision}
\section{Final remarks}

>>>>

\setbeamertemplate{caption}[numbered]
\setbeamertemplate{theorems}[numbered]

% TODO theorems/definitions etc should be numbered

% TODO itemize dots seem to be lost

@@

\section{Additional metadata for tpo revision}

\begin{frame}{Enriching Epistemic States}
    \note{
        \begin{itemize}
            \item W+-
        \end{itemize}
    }
\end{frame}

\begin{frame}{$\leq$-faithful tpo}
    \begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ \cite{Booth2011}]
        \label{definition:faithful-tpo}Let $\preceq \subseteq W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
    \end{definition}
    \note{
        \begin{itemize}
            \item characteristics + definition
        \end{itemize}
    }
\end{frame}

\begin{frame}[fragile]{$\leq$-faithful tpo visualisation}
    \begin{figure}[H]
        \centering
        \begin{tikzpicture}[scale=1]
            \begin{axis}[
                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
                  xticklabels={,,},
                  ytick style={draw=none},
                  xtick style={draw=none},
                  axis line style={draw=none}
            ]
            \addplot[
                scatter,
                scatter src=explicit symbolic,
                mark size=3,
                scatter/classes={
                    empty={mark=*, fill=white},
                    filled={mark=*, fill=black}
                },
                nodes near coords*={\Label},
                visualization depends on={value \thisrow{label} \as \Label}
            ]
            table [meta=class] {
                    x y class label

                    3 1 empty $x_{4}^{+}$
                    6 1 empty $x_{4}^{-}$

                    2 2 empty $x_{3}^{+}$
                    5 2 empty $x_{3}^{-}$

                    1 3 empty $x_{2}^{+}$
                    3 3 empty $x_{2}^{-}$

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
            };
            \end{axis}
        \end{tikzpicture}
        \caption{Representation of $\preceq$ over $W^{\pm}$ using intervals}
        \label{fig:example-visualisation-scatterplot}
    \end{figure}

    \note{
        \begin{itemize}
            \item example with sticks
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: $\leq$-faithful tpo}
    \note{
        \begin{itemize}
            \item example for courtroom
        \end{itemize}
    }
\end{frame}

\section{Booth and Meyer tpo-revision operators}

\begin{frame}{BM tpo-revision operator}
    \note{
        \begin{itemize}
            \item definition
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: Revision}
    \note{
        \begin{itemize}
            \item example 7, math
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: Revision Visualised}
    \note{
        \begin{itemize}
            \item example 7, figure 4
        \end{itemize}
    }
\end{frame}

\begin{frame}{BACKUP: non-prioritised revision}
    \note{
        \begin{itemize}
            \item example 7, figure 4
        \end{itemize}
    }
\end{frame}

\begin{frame}{Properties of BM Revision Operators}
    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
        \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
        \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
        \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
        \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
        \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
        \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
    \end{enumerate}

    \note{
        \begin{itemize}
            \item properties
        \end{itemize}
    }
\end{frame}

\begin{frame}{Family of BM Revision Operators}
    \begin{theorem}
        \label{theorem:revision-operator}Let $\ast$ be any revision operator for $\leq$. Then $\ast$ is generated from some $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ iff $\ast$ satisfies \ref{AST1}-\ref{AST7}. \cite{Booth2011}
    \end{theorem}

    \note{
        \begin{itemize}
            \item theorem 1
        \end{itemize}
    }
\end{frame}

\section{Iterating: $\preceq$-revision}

\begin{frame}{A concrete operator}
    \note{
        \begin{itemize}
            \item math for operator
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: A concrete operator}
    \note{
        \begin{itemize}
            \item math for example with operator
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Visualised}
    \note{
        \begin{itemize}
            \item figure 6
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Conditional beliefs 1}
    \note{
        \begin{itemize}
            \item figure 7
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Conditional beliefs 2}
    \note{
        \begin{itemize}
            \item figure 8
        \end{itemize}
    }
\end{frame}

\section{Final remarks}
